Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-02-23 paper.tex
Local changes

%
% TODO: explicar los resultados obtenidos en la selección de variables: 
%  (1) con el SOM, (2) con los métodos de selecc. vars.
%
% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
% - se ha usado la implementación de estos 5 métodos del paquete WEKA
% - se han realizado 30 ejecuciones con cada método
% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
To do so, in a first stage, the feature selection process has been carried out 
using both the CfsSubsetEval \cite{Hall1998} (a correlation-based feature subset 
evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
adaptation of relief for attribute estimation) evaluation methods, implemented 
in the Weka tool.

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the ReliefFAttributeEval feature selection method, and taking into account 
the best ranked attributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 
1st year, reprints, units distributed as novelty, weeks for sale, total sales}.

% con CfsSubsetEval salen seleccionadas (4):
% num_reprints tot_points_sale print_run + total_sales
Using the CfsSubsetEval feature selection method, the following variables have 
been selected: \emph{number of reprints, total points of sale, print-run, total sales}.
%FERGU: podeis quitar estos parrafos de variables porque ya está la tabla :)

%*************************************** SOM ANALISYS
% como tercer método, se ha usado el SOM; tras interpretar los mapas, se
% seleccionaron las variables más adecuadas.
Then, an exhaustive analysis of the SOM results was carried out in order to 
determine the best variables to be considered to build the forecasting model.

@@

Table \ref{tabla:resultsT} shows obtained results (time to build the model and 
error) after applying the proposed forecasting methods on the original dataset,
using the 16 available variables per book.
In this dataset, every book is described using not only numerical variables, 
but using two additional categorical variables, \emph{editorial} and \emph{collection}, 
what makes harder to process the instances and build the different models.

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[ht]
\caption{Results (errors and time) obtained using the different forecasting
methods on the original dataset (16 variables per book). In this case,
due to the categorical variables, the MLP could not be run.}
\label{tabla:resultsT}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Base & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
\hline 
\hline 
M5P & 0.9076 & \textbf{202.1547} & 591.0257 & \textbf{35.31}\% & 42.10\% & 39.73\tabularnewline
\hline 
LR & 0.9204 & 255.0526 & 548.0975 & 44.5527 & 39.10\% & 0.03\tabularnewline
\hline 
SVM & \textbf{0.9402} & 203.4416 & \textbf{481.7528} & 35.54\% & \textbf{34.37}\% & 308.31\tabularnewline
\hline 
kNN & 0.7273 & 310.4078 & 993.2663 & 54.22\% & 70.85\% & 0\tabularnewline
\hline 
MLP & 0.9197 & 289.7393 & 585.6445 & 50.61\% & 41.78\% & 82.08\tabularnewline
\hline 
\end{tabular}
\end{table*}

>>>>

%
% TODO: explicar los resultados obtenidos en la selección de variables: 
%  (1) con el SOM, (2) con los métodos de selecc. vars.
%
% CONTAR COMO SE HAN PLANIFICADO LAS EJECUCIONES CON LOS DIFERENTES METODOS:
% - se ha usado la implementación de estos 5 métodos del paquete WEKA
% - se han realizado 30 ejecuciones con cada método
% - se ha usado una máquina Linux, Intel(R) Core(TM) i5-4430 CPU at 3.00GHz (4 cores) and 16 GB RAM
To do so, in a first stage, the feature selection process has been carried out 
using both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset 
evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an 
adaptation of relief for attribute estimation) evaluation methods, implemented 
in the Weka tool.

% con ReliefFAttributeEval salen seleccionadas (9):
% print_run num_reprints tot_points_sale tot_points_sale_1st_year reprints distrib_novelty weeks_sale + total_sales
Using the {\tt ReliefFAttributeEval} feature selection method, and taking into account 
the best ranked attributes, the following variables have been selected: 
\emph{print-run, number of reprints, total points of sale, total points of sale 
1st year, reprints, units distributed as novelty, weeks for sale, total sales}.

% con CfsSubsetEval salen seleccionadas (4):
% num_reprints tot_points_sale print_run + total_sales
Using the {\tt CfsSubsetEval} feature selection method, the following variables have 
been selected: \emph{number of reprints, total points of sale, print-run, total sales}.
%FERGU: podeis quitar estos parrafos de variables porque ya está la tabla :)

%*************************************** SOM ANALISYS
% como tercer método, se ha usado el SOM; tras interpretar los mapas, se
% seleccionaron las variables más adecuadas.
Then, an analysis of the SOM results has been carried out in order to 
determine the best variables to be considered to build the forecasting model.

@@

Table \ref{tabla:resultsT} shows obtained results (time to build the model and 
error) after applying the proposed forecasting methods on the original dataset,
using the 16 variables that describe each book.
In this dataset, every book is described using not only numerical variables, 
but also two additional categorical variables, \emph{editorial} and \emph{collection}, 
which could, a priori, make harder to process the instances and build the different models.

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
% OK
\begin{table*}[ht]
\caption{Results (errors and time) obtained using the different forecasting
methods on the original dataset (16 variables per book). In this case,
due to the categorical variables, the MLP could not be run.}
\label{tabla:resultsT}
\centering{}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
Base & Correlation coefficient (\%) & MAE & RMSE & RAE(\%) & RRSE (\%) & Time(sec)\tabularnewline
\hline 
\hline 
M5P & 0.9076 & \textbf{202.1547} & 591.0257 & \textbf{35.31}\% & 42.10\% & 39.73\tabularnewline
\hline 
LR & 0.9204 & 255.0526 & 548.0975 & 44.5527 & 39.10\% & 0.03\tabularnewline
\hline 
SVM & \textbf{0.9402} & 203.4416 & \textbf{481.7528} & 35.54\% & \textbf{34.37}\% & 308.31\tabularnewline
\hline 
kNN & 0.7273 & 310.4078 & 993.2663 & 54.22\% & 70.85\% & 0\tabularnewline
\hline 
MLP & 0.9197 & 289.7393 & 585.6445 & 50.61\% & 41.78\% & 82.08\tabularnewline
\hline 
\end{tabular}
\end{table*}
